---
title: "Ecoregion Report"
author: "Deepa Filatow"
date: "May 25, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Ecosection of British Columbia

Below is a map of the ecosections coloured by ecosection code.

```{r loadlibraries, include = FALSE}
library (bcdata)
library (sf)
library (raster)
library (fasterize)
library (leaflet)
alb = 3005
ecosections <- bcdc_get_data("ccc01f43-860d-4583-8ba4-e72d8379441e", crs = alb)
elev <- raster("C:/Users/dfilatow/Documents/GISdownloads/HABC/elev.tif")
plot (ecosections["ECOSECTION_CODE"])
```


```{r ecosectionname, include=FALSE}
es.name <- "Elk Valley"
#ecosections$ELEV_MAX <- raster::extract(elev, ecosections, fun = max)
#plot (ecosections["ELEV_MAX"])
#es.r <- fasterize(ecosections, elev,field = "OBJECTID")
#test <- zonal(elev, es.r)
#plot(test)

```

### Ecosection Topography

Here is a map of the `r es.name` Ecosection showing the 1 ha mean elevation.

```{r elevecosection}

es <- filter(ecosections, ECOSECTION_NAME == as.character(es.name))
es.elev <- elev %>% raster::crop(es) %>% mask(es)
plot(es.elev)

```

This is a histogram of the 1 ha elevation in the ecosection.

```{r elevhistogram}
hist(es.elev)
```

### Biogeoclimatic Units

Here is a map of the biogeoclimatic zone/subzone/varients in the `r es.name` Ecosection.

```{r bec}
bec <- bcdc_query_geodata ("f358a53b-ffde-4830-a325-a5a03ff672c3", crs = alb) %>% 
  filter(INTERSECTS(es)) %>% 
  collect() %>% st_intersection(es)
plot(bec["MAP_LABEL"])
```

This is the end of the demo.